A 38 Million Year Old Mini-Neptune in the Kepler Field

### 2021-09-14 paper/ms.tex
update ms
Co-authored-by: Motohide Tamura <motohide.tamura@nao.ac.jp>

A previous clustering analysis of the Gaia data reported that
Kepler\,1627 (KIC 6184894; KOI 5245; TIC 120105470) is a member of the
\cn\ \citep{kounkel_untangling_2019}.  Given the previous statistical
validation the close-in mini-Neptune Kepler 1627b
\citep{2012ApJS..199...24T,morton_false_2016,thompson_planetary_2018},
we examined the age of the star and its putative host cluster more
closely (Section~\ref{sec:cluster}).  We find that the $\delta$ Lyr
cluster is \clusterage\ old, and that \sn\ is indeed a member of the
cluster.  Focusing on the planet itself, we confirm that despite the
presence of a previously unreported binary companion, the planet
orbits the G-dwarf primary on an orbit that is likely aligned with the
stellar rotation axis (Section~\ref{sec:planet}).  We conclude by
highlighting broader implications for our ability to age-date a
statistical sample of planets (Section~\ref{sec:conc}).

@@

		\vspace{-0.5cm}
		\subfloat{
			\includegraphics[width=0.8\textwidth]{f15c.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf The \cn\ is \clusterage\ old.}  {\it Top:}
    Color-absolute magnitude diagram of candidate \cn\ members, in addition to
    stars in IC\,2602 ($\approx38$\,Myr), the Pleiades ($\approx
    115$\,Myr; \citealt{dahm_2015}), and the Gaia EDR3 Catalog of
    Nearby Stars (gray background).  The right panel is a
    zoomed view of the pre-main-sequence.  The \cn\ and IC\,2602 are
    approximately the same isochronal age.  {\it Bottom:} TESS and
    Kepler stellar rotation periods versus dereddened Gaia colors,
    with the Pleiades and Praesepe (650\,Myr) shown for reference
    \citep{rebull_rotation_2016a,douglas_poking_2017}.  Most
    candidate \cn\ members are gyrochronally younger than the
    Pleiades; outliers are probably field interlopers.
   \label{fig:age}
	}
\end{figure*}

@@

In summary, the age of the \cn\ cluster based on the empirical
pre-main-sequence interpolation method is \clusterage.  This method
hinges on the age adopted for IC\,2602, since it is the closest
reference cluster in the color-absolute magnitude diagram.
Gyrochronologically, while most of the FGK dwarfs in the \cn\ have
not yet converged to a slow sequence, their rotation periods 
are generally consistent with an $\approx$38\,Myr age. The most
precise age for \sn\ and its planet are therefore identical to the cluster,
based on the star's spatial and kinematic association with the
cluster, and the assumption that the planet formed shortly after
the star.

@@

If the \pn\ transit signal is created by a bonafide planet,  then to
our knowledge its age would make it the youngest planet yet found by
the main Kepler mission.\footnote{The re-purposed K2
mission however has found two younger systems: K2-33b and V1298 Tau
\citep{David_et_al_2017,Mann_K2_33b_2016,david_four_2019}}  A portion
of the light curve is shown with the phase-folded transit in
Figure~\ref{fig:lc}.  The \texttt{PDCSAP}
photometry is dominated by a quasi-periodic starspot signal with a peak-to-peak
amplitude that varies between 2\% and 8\%, depending on the degree of
asymmetry in spot coverage between the stellar hemispheres.  The
starspot signal repeats every $2.642\pm0.042$\,days, where the
uncertainty is based on the scatter observed between different Kepler
quarters.  The details of how we model the starspot signal to derive
the parameters of the planet are discussed in
Appendix~\ref{app:gptransit}.  The stellar parameters are listed in
Table~\ref{tab:starparams}; the stellar mass, radius, and effective
temperature are found by interpolating against a 38$\,$Myr MIST
isochrone.  The systematic uncertainties are taken to be the
difference in parameters from the PARSEC isochrones, and the reported
uncertainties are a quadrature sum of the statistical and systematic
components.  The transit-fitting results, given in
Table~\ref{tab:posterior}, are consistent with a mini-Neptune sized
planet ($3.34\pm 0.18\,R_\oplus$) on a close-in circular\footnote{Our
transit fitting yields $e<0.48$ at 2-$\sigma$; the constraints on the
eccentricity are not particularly strong.} orbit around a G8V star
($0.88 \pm 0.02 R_\odot$).

Could the transit signal be produced by anything other than a planet
orbiting this near-solar analog?  \citet{morton_false_2016} validated
the planet based on the transit shape, arguing that the most probable 
false positive scenario was that of a background eclipsing binary,
which had a model-dependent probability of $\approx10^{-5}$.
As we describe in Appendix~\ref{app:companionstar} however,
the system has a low-mass stellar companion ($M_{\rm B}\approx
0.44\,M_\odot$), and so we reconsidered this false positive scenario
in some detail.

@@

The final piece of evidence comes from a spectroscopic transit we
observed using Keck/HIRES during the night of 7 Aug 2021.  We
used the iodine cell for the wavelength calibration, and scheduled the
transit using the ephemeris of \citet{holczer_transit_2016}.  We also acquired
simultaneous multi-band photometry using MuSCAT3 \citep{Narita_2020}.
The lower panels in Figure~\ref{fig:obliquity} show the results.  The
photometry shows the expected starspot trend, along with the transit
and a likely starspot crossing event at ${\rm JD} - 2459433 = 0.955$.
The radial velocities show significant scatter, and an
increase in RV is seen shortly after the expected ingress time.  The
internal uncertainty on the RVs ($\approx 15\,{\rm m\,s}^{-1}$) is
dominated by the $v\sin i$ broadening.

@@

We fitted the RVs using the \citet{hirano_analytic_2010,hirano_2011}
models for the Rossiter-McLaughlin (RM) effect, and allowed the
sky-projected obliquity, the stellar equatorial velocity, and the
Gaussian dispersion of the spectral lines to vary.  We also allowed
for an optional linear and quadratic trend, and a white-noise jitter
term.  The quadratic model with the RM effect is shown in
Figure~\ref{fig:obliquity}; the prior on $v\sin i$ has been assumed
from Table~\ref{tab:starparams}, and the jitter term has been
incorpoarted.
We found $\chi^2_{\rm red} =
5.4$ for the best-fitting linear case, and $\chi^2_{\rm red} = 4.4$
for the best-fitting quadratic, with a $\Delta {\rm BIC} = {\rm
BIC}_{\rm line} - {\rm BIC}_{\rm quad} = 19.6$ and $\Delta {\rm AIC} =
{\rm AIC}_{\rm line} - {\rm AIC}_{\rm quad} = 20.6$.  While this
provides strong statistical evidence to prefer the quadratic model
over the linear one, the $\chi^2_{\rm red}$ indicate that neither fit
is very good.  Considering a quadratic trend without any RM
effect yields $\chi^2_{\rm red} = 4.3$, and $\Delta {\rm BIC} = {\rm
BIC}_{\rm trend} - {\rm BIC}_{\rm quad} = 1.9$ ($\Delta {\rm
AIC}=5.2$).  From a model-comparison standpoint, there is therefore
only marginal statistical evidence to prefer the best-fitting ``RM and
quadratic trend'' model over the best-fitting ``quadratic trend only''
model.  Given the expected semi-amplitude of the velocity anomaly
($\Delta v_{\rm RM}\approx 20\,{\rm m\,s}^{-1}$) and the achieved precision,
we cannot claim a detection of the Doppler transit.
From the MuSCAT3 data however, we do know that the transit
was observed, and the increase in radial velocity seen shortly after
ingress is more consistent with a prograde or polar orbit than a
retrograde orbit.  Fixing the orbit to be either exactly prograde or
exactly retrograde, we find $\Delta {\rm BIC} = {\rm BIC}_{\rm
retrograde} - {\rm BIC}_{\rm trend} = 18.0$; the retrograde case is
ruled out on this basis.
% More data will be needed however to
% make a more precise measurement of the stellar obliquity.

@@

The authors are grateful to T{.}~David for help with the transit
fitting, to R{.}~Kerr for kindly providing us with the
\citet{Kerr2021} membership list prior to its publication, and to
J{.}~Winn for helpful discussions on the RM observations and flare
timing.
The authors are also grateful to K{.}~Collins for
helping resolve the scheduling conflict that would have otherwise
prevented the MuSCAT3 observations.
% is grateful to G.~Zhou, B{.}~Tofflemire, A{.}~McWilliam,
% E{.}~Newton, M{.}~Kounkel, A{.}~Kraus, L{.}~Hillenbrand, and
% K{.}~Hawkins for the discussions on young stars, rotation, and lithium
% that encouraged this analysis.
%
L.G.B{.} acknowledges support from a Charlotte Elizabeth Procter
Fellowship from Princeton University, as well as from the TESS GI Program, programs
G011103 and G022117, through NASA grants 80NSSC19K0386 and
80NSSC19K1728.
%
%
Keck/NIRC2 imaging was acquired by programs 2015A/N301N2L
(PI: A.~Kraus) and 2019A/N069 (PI: E.~Petigura).
%
In addition, this paper is based in part on observations made with the
MuSCAT3 instrument, developed by the Astrobiology Center and under
financial supports by JSPS KAKENHI (JP18H05439) and JST PRESTO
(JPMJPR1775), at Faulkes Telescope North on Maui, HI, operated by the
Las Cumbres Observatory.
%
This work is partly supported by JSPS KAKENHI Grant Numbers 22000005,
JP15H02063, JP17H04574, JP18H05439, JP18H05442, JST PRESTO Grant
Number JPMJPR1775, the Astrobiology Center of National Institutes of
Natural Sciences (NINS) (Grant Number AB031010).
%
% ACKNOWLEDGE PFS / CAMPANAS.
%
This paper also includes data collected by the TESS mission, which are
publicly available from the Mikulski Archive for Space Telescopes
(MAST).
%
Funding for the TESS mission is provided by NASA's Science Mission
directorate.
%
We thank the TESS Architects (G.~Ricker, R.~Vanderspek, D.~Latham,
S.~Seager, J.~Jenkins) and the many TESS team members for their
efforts to make the mission a continued success.
%
%
%This study was based in part on observations at Cerro Tololo
%Inter-American Observatory at NSF's NOIRLab (NOIRLab Prop{.} ID
%2020A-0146; 2020B-0029 PI: Bouma), which is managed by the
%Association of Universities for Research in Astronomy (AURA) under a
%cooperative agreement with the National Science Foundation.
%
%
Finally, this research has made use of the Keck Observatory Archive (KOA),
which is operated by the W. M. Keck Observatory and the NASA Exoplanet
Science Institute (NExScI), under contract with the National
Aeronautics and Space Administration.  We also thank the Keck
Observatory staff for their support of HIRES and remote observing.  We
recognize the importance that the summit of Maunakea has within the
indigenous Hawaiian community, and are deeply grateful to have the
opportunity to conduct observations from this mountain.
%
% The Digitized Sky Survey was produced at the Space Telescope Science
% Institute under U.S. Government grant NAG W-2166.
% Figure~\ref{fig:scene} is based on photographic data obtained using
% the Oschin Schmidt Telescope on Palomar Mountain.
%

@@

Figure~\ref{fig:XYZvtang} shows stars reported by
\citet{kounkel_untangling_2019} to be in the group ``Theia 73'', which
was cross-matched by Kounkel \& Covey as being ``Stephenson 1''.
\citet{kounkel_untangling_2019} reported \noriginal\ stars to be
present in this cluster.  For our Figure, galactic positions were
calculated and plotted only for stars with parallax signal-to-noise
exceeding 20.  The location of the Sun is shown on the plots.  The
smattering of reported cluster members (gray and black points) has a
significantly different structure that the cluster initially
identified by \citet{stephenson_possible_1959} and corroborated by
\citet{eggen_photometric_1968}.  While the non-uniform ``clumps''
might be part of a real structure, they could also be an artifact of
the data processing steps performed by
\citet{kounkel_untangling_2019}.  We therefore opted to only consider
stars in the immediate kinematic and spatial vicinity of \sn.  The
tangential velocities relative to \sn\ are shown in the bottom right
panel.  These are computed by assuming that every star has the same
three-dimensional spatial velocity as \sn, where we assume a systemic
radial velocity of $-16.7 \pm 0.2$\,\kms\ based on the HIRES
spectra.  The
relevant projection effects are then taken into account, as discussed
by {\it e.g.}, \citet{Meingast2021} and \citet{bouma_2021_ngc2516}.
We performed the actual selection by then manually drawing lassos with
the interactive \texttt{glue} visualization tool
\citep{beaumont_2014_13866} in the four projections shown in
Figure~\ref{fig:XYZvtang}.  While bonafide members likely exist
outside of our selection region (and our selection also includes some
field star interlopers), our aim is to verify the existence of the
cluster in the vicinity of Kepler\,1627, and to measure its age.  The
procedure we have adopted enables both tasks.

@@

		\vspace{-0.1cm}
		\subfloat{
			\includegraphics[width=0.55\textwidth]{f6.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Kepler 1627 is a binary.} {\it Top:} High-resolution imaging
    from Gemini-North/`Alopeke ({\it left}) and Keck/NIRC2 ({\it
    right}) shows an $\approx$M2V companion at $\rho \approx
    0\farcs16$, which corresponds to a projected separation of
    $53\pm4$\,AU.  {\it Bottom:} Gaia EDR3 renormalized unit weight
    error (RUWE) point estimates for Kepler\,1627A and other members
    of the $\delta$\,Lyr cluster reported by \citet{KounkelCovey2019}.
    Since other members of the cluster with similar colors have
    comparable degrees of photometric variability, the high RUWE
    suggests that Kepler\,1627 is an astrometric binary. 
    \label{fig:kep1627binary}
	}
\end{figure*}

We first noted the presence of a stellar neighbor in archival
Keck/NIRC2 Kp-band adaptive optics imaging (2.12\,$\mu $m), from the
Spring semesters of both 2015 and 2019.  We acquired additional
Gemini-North/`Alopeke speckle imaging on 24 June 2021, which showed
the same companion in the 0.83\,$\mu$m notch filter, but not the
$0.56\,\mu$m filter.  Figure~\ref{fig:kep1627binary} summarizes the
results of the high-resolution imaging.  Although the companion is
unresolved in the Gaia source catalog, its existence was also
suggested by the primary star's large RUWE, relative to other members
of the \cn.  The images yield a projected separation $\rho \approx
0\farcs16$, with $\Delta m_{832} \approx 3.1$ and $\Delta m_{\rm Kp} =
2.5$.  Using the measured Gaia EDR3 parallax for the system, this
implies a projected separation of $53 \pm 4$.  Given the large
observed RUWE of the primary, and the low geometric probability that a
companion imaged within $\rho \approx 0\farcs16$ is a chance
line-of-sight companion, we proceed under the assumption that the
companion is bound, and that Kepler\,1627 system is a binary.  Based
on the
tabulation\footnote{\url{http://www.pas.rochester.edu/~emamajek/EEM_dwarf_UBVIJHK_colors_Teff.txt},
version \texttt{2021/03/02}.} by \citet{pecaut_mamajek_2013}, the
measured magnitude differences for a G8V primary correspond to a
spectral type for the companion of $\approx$M2V ($M_\star \approx
0.44\,M_\odot$).  However, the companion should have a longer
pre-main-sequence contraction phase than the primary, which would
imply that this mass is overestimated by $\sim10$ to $20\%$.

>>>>

A previous clustering analysis of the Gaia data reported that
Kepler\,1627 (KIC 6184894; KOI 5245; TIC 120105470) is a member of the
\cn\ \citep{kounkel_untangling_2019}.  Given the previous statistical
validation the close-in mini-Neptune Kepler 1627b
\citep{2012ApJS..199...24T,morton_false_2016,thompson_planetary_2018},
we examined the age of the star and its putative host cluster more
closely (Section~\ref{sec:cluster}).  We find that the $\delta$ Lyr
cluster is \clusterage\ old, and that \sn\ is indeed a member of the
cluster.  Focusing on the planet itself, we confirm that despite the
presence of a previously unreported binary companion, hereafter
Kepler\,1627B, the planet orbits the G-dwarf primary on an orbit that
is likely aligned with the stellar rotation axis
(Section~\ref{sec:planet}).  We conclude by highlighting broader
implications for our ability to age-date a statistical sample of
planets (Section~\ref{sec:conc}).

@@

		\vspace{-0.5cm}
		\subfloat{
			\includegraphics[width=0.8\textwidth]{f15c.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf The \cn\ is \clusterage\ old.}  {\it Top:}
    Color-absolute magnitude diagram of candidate \cn\ members, in addition to
    stars in IC\,2602 ($\approx38$\,Myr), the Pleiades ($\approx
    115$\,Myr; \citealt{dahm_2015}), and the Gaia EDR3 Catalog of
    Nearby Stars (gray background).  The zoomed right panel
    highlights the pre-main-sequence.  The \cn\ and IC\,2602 are
    approximately the same isochronal age.  {\it Bottom:} TESS and
    Kepler stellar rotation period versus dereddened Gaia color,
    with the Pleiades and Praesepe (650\,Myr) shown for reference
    \citep{rebull_rotation_2016a,douglas_poking_2017}.  Most
    candidate \cn\ members are gyrochronally younger than the
    Pleiades; outliers are probably field interlopers.
   \label{fig:age}
	}
\end{figure*}

@@

In summary, the age of the \cn\ based on the empirical
pre-main-sequence interpolation method is \clusterage.  This method
hinges on the age adopted for IC\,2602, since it is the closest
reference cluster in the color-absolute magnitude diagram.
Gyrochronologically, while most of the FGK dwarfs in the \cn\ have
not yet converged to a slow sequence, their rotation periods 
are generally consistent with an $\approx$38\,Myr age. The most
precise age for \sn\ and its planet are therefore identical to the cluster,
based on the star's spatial and kinematic association with the
cluster, and the assumption that the planet formed shortly after
the star.

@@

If the \pn\ transit signal is created by a genuine planet,  then to
our knowledge its age would make it the youngest planet yet found by
the main Kepler mission.\footnote{The re-purposed K2 mission however
has found two younger systems containing five planets: K2-33b ($9\pm1\,{\rm Myr}$;
\citealt{Mann_K2_33b_2016,David_et_al_2017}) and V1298 Tau
($23\pm4\,{\rm Myr}$; \citealt{david_four_2019}).}  A portion of the
light curve is shown with the phase-folded transit in
Figure~\ref{fig:lc}.  The \texttt{PDCSAP} photometry is dominated by a
quasi-periodic starspot signal with a peak-to-peak amplitude that
varies between 2\% and 8\%, depending on the degree of asymmetry in
spot coverage between the stellar hemispheres.  The starspot signal
repeats every $2.642\pm0.042$\,days, where the uncertainty is based on
the scatter observed between different Kepler quarters.  The details
of how we model the starspot signal to derive the parameters of the
planet are discussed in Appendix~\ref{app:gptransit}.  The stellar
parameters are listed in Table~\ref{tab:starparams}; the stellar mass,
radius, and effective temperature are found by interpolating against a
38$\,$Myr MIST isochrone.  The systematic uncertainties are taken to
be the difference in parameters from the PARSEC isochrones, and the
reported uncertainties are a quadrature sum of the statistical and
systematic components.  The transit-fitting results, given in
Table~\ref{tab:posterior}, are consistent with a mini-Neptune sized
planet ($3.34\pm 0.18\,R_\oplus$) on a close-in circular\footnote{Our
transit fitting yields $e<0.48$ at 2-$\sigma$; the constraints on the
eccentricity are not particularly strong.} orbit around a G8V star
($0.88 \pm 0.02 R_\odot$).

Could the transit signal be produced by anything other than a planet
orbiting this near-solar analog?  \citet{morton_false_2016} validated
the planet based on the transit shape, arguing that the most probable 
false positive scenario was that of a background eclipsing binary,
which had a model-dependent probability of $\approx10^{-5}$.
As we describe in Appendix~\ref{app:companionstar} however,
Kepler\,1627A is accompanied by a low-mass stellar companion ($M_{\rm
B}\approx 0.44\,M_\odot$).  We therefore reconsidered this false
positive scenario in some detail.

@@

The final piece of evidence comes from a spectroscopic transit we
observed using Keck/HIRES during the night of 7 Aug 2021.  We
used the iodine cell for wavelength calibration, and scheduled the
transit using the ephemeris of \citet{holczer_transit_2016}.  We also acquired
simultaneous multi-band photometry using MuSCAT3 \citep{Narita_2020}.
The lower panels in Figure~\ref{fig:obliquity} show the results.  The
photometry shows the expected starspot trend, along with the transit
and a likely starspot crossing event at ${\rm JD} - 2459433 = 0.955$.
The radial velocities show significant scatter, and an
increase in RV is seen shortly after the expected ingress time.  The
internal uncertainty on the RVs ($\approx 15\,{\rm m\,s}^{-1}$) is
dominated by the $v\sin i$ broadening.

@@

We fitted the RVs using the \citet{hirano_analytic_2010,hirano_2011}
models for the Rossiter-McLaughlin (RM) effect, and allowed the
sky-projected obliquity, the stellar equatorial velocity, and the
Gaussian dispersion of the spectral lines to vary.  We also allowed
for an optional linear and quadratic trend, and a white-noise jitter
term.  The quadratic model with the RM effect is shown in
Figure~\ref{fig:obliquity}; the prior on $v\sin i$ has been assumed
from Table~\ref{tab:starparams}, and the jitter term has been
incorporated.
We found $\chi^2_{\rm red} =
5.4$ for the best-fitting linear case, and $\chi^2_{\rm red} = 4.4$
for the best-fitting quadratic, with a $\Delta {\rm BIC} = {\rm
BIC}_{\rm line} - {\rm BIC}_{\rm quad} = 19.6$ and $\Delta {\rm AIC} =
{\rm AIC}_{\rm line} - {\rm AIC}_{\rm quad} = 20.6$.  While this
provides strong statistical evidence to prefer the quadratic model
over the linear one, the $\chi^2_{\rm red}$ indicate that neither fit
is very good.  Considering a quadratic trend without any RM
effect yields $\chi^2_{\rm red} = 4.3$, and $\Delta {\rm BIC} = {\rm
BIC}_{\rm trend} - {\rm BIC}_{\rm quad} = 1.9$ ($\Delta {\rm
AIC}=5.2$).  From a model-comparison standpoint, there is therefore
only marginal statistical evidence to prefer the best-fitting ``RM and
quadratic trend'' model over the best-fitting ``quadratic trend only''
model.  Given the expected semi-amplitude of the velocity anomaly
($\Delta v_{\rm RM}\approx 20\,{\rm m\,s}^{-1}$) and the achieved precision,
we cannot claim a detection of the Doppler transit.
From the MuSCAT3 data however, we do know that the transit
was observed, and the increase in radial velocity seen shortly after
ingress is more consistent with a prograde or polar orbit than a
retrograde orbit.  Fixing the orbit to be either exactly prograde or
exactly retrograde, we find $\Delta {\rm BIC} = {\rm BIC}_{\rm
retrograde} - {\rm BIC}_{\rm trend} = 18.0$; the retrograde case is
ruled out on this basis.
% More data will be needed however to
% make a more precise measurement of the stellar obliquity.

@@

The authors are grateful to T{.}~David, J{.}~Winn, and A{.}~Howard for
illuminating discussions and guidance, and to R{.}~Kerr for kindly
providing us with the \citet{Kerr2021} membership list prior to its
publication.
The authors are also grateful to K{.}~Collins for
helping resolve the scheduling conflict that would have otherwise
prevented the MuSCAT3 observations.
% is grateful to G.~Zhou, B{.}~Tofflemire, A{.}~McWilliam,
% E{.}~Newton, M{.}~Kounkel, A{.}~Kraus, L{.}~Hillenbrand, and
% K{.}~Hawkins for the discussions on young stars, rotation, and lithium
% that encouraged this analysis.
%
L.G.B{.} acknowledges support from a Charlotte Elizabeth Procter
Fellowship from Princeton University, as well as from the TESS GI Program, programs
G011103 and G022117, through NASA grants 80NSSC19K0386 and
80NSSC19K1728.
%
%
Keck/NIRC2 imaging was acquired by programs 2015A/N301N2L
(PI: A.~Kraus) and 2019A/N069 (PI: E.~Petigura).
%
In addition, this paper is based in part on observations made with the
MuSCAT3 instrument, developed by the Astrobiology Center and under
financial supports by JSPS KAKENHI (JP18H05439) and JST PRESTO
(JPMJPR1775), at Faulkes Telescope North on Maui, HI, operated by the
Las Cumbres Observatory.
%
This work is partly supported by JSPS KAKENHI Grant Numbers 22000005,
JP15H02063, JP17H04574, JP18H05439, JP18H05442, JST PRESTO Grant
Number JPMJPR1775, the Astrobiology Center of National Institutes of
Natural Sciences (NINS) (Grant Number AB031010).
%
% ACKNOWLEDGE PFS / CAMPANAS.
%
This paper also includes data collected by the TESS mission, which are
publicly available from the Mikulski Archive for Space Telescopes
(MAST).
%
Funding for the TESS mission is provided by NASA's Science Mission
directorate.
%
We thank the TESS Architects (G.~Ricker, R.~Vanderspek, D.~Latham,
S.~Seager, J.~Jenkins) and the many TESS team members for their
efforts to make the mission a continued success.
%
%
%This study was based in part on observations at Cerro Tololo
%Inter-American Observatory at NSF's NOIRLab (NOIRLab Prop{.} ID
%2020A-0146; 2020B-0029 PI: Bouma), which is managed by the
%Association of Universities for Research in Astronomy (AURA) under a
%cooperative agreement with the National Science Foundation.
%
%
Finally, this research has made use of the Keck Observatory Archive (KOA),
which is operated by the W. M. Keck Observatory and the NASA Exoplanet
Science Institute (NExScI), under contract with the National
Aeronautics and Space Administration.  We also thank the Keck
Observatory staff for their support of HIRES and remote observing.  We
recognize the importance that the summit of Maunakea has within the
indigenous Hawaiian community, and are deeply grateful to have the
opportunity to conduct observations from this mountain.
%
% The Digitized Sky Survey was produced at the Space Telescope Science
% Institute under U.S. Government grant NAG W-2166.
% Figure~\ref{fig:scene} is based on photographic data obtained using
% the Oschin Schmidt Telescope on Palomar Mountain.
%

@@

Figure~\ref{fig:XYZvtang} shows stars reported by
\citet{kounkel_untangling_2019} to be in the group ``Theia 73'', which
was cross-matched by Kounkel \& Covey as being ``Stephenson 1''.
\citet{kounkel_untangling_2019} reported \noriginal\ stars to be
present in this cluster.  For our Figure, galactic positions were
calculated and plotted only for stars with parallax signal-to-noise
exceeding 20.  The location of the Sun is shown on the plots.  The
smattering of reported cluster members (gray and black points) has a
significantly different structure that the cluster initially
identified by \citet{stephenson_possible_1959} and corroborated by
\citet{eggen_photometric_1968}.  While the non-uniform ``clumps''
might be part of a real structure, they could also be an artifact of
the data processing steps performed by
\citet{kounkel_untangling_2019}.  We therefore opted to only consider
stars in the immediate kinematic and spatial vicinity of \sn.  The
tangential velocities relative to \sn\ are shown in the bottom right
panel.  These are computed by assuming that every star has the same
three-dimensional spatial velocity as \sn, where we assume a systemic
radial velocity of $-16.7 \pm 0.2$\,\kms\ based on the HIRES
spectra.  The
relevant projection effects are then taken into account, as discussed
by {\it e.g.}, \citet{Meingast2021} and \citet{bouma_2021_ngc2516}.
We performed the actual selection by then manually drawing lassos with
the interactive \texttt{glue} visualization tool
\citep{beaumont_2014_13866} in the four projections shown in
Figure~\ref{fig:XYZvtang}.  While cluster members likely exist
outside of our selection region (and our selection also includes some
field star interlopers), our aim is to verify the existence of the
cluster in the vicinity of Kepler\,1627, and to measure its age.  The
procedure we have adopted enables both tasks.

@@

		\vspace{-0.1cm}
		\subfloat{
			\includegraphics[width=0.55\textwidth]{f6.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Kepler 1627 is a binary.} {\it Top:} High-resolution imaging
    from Gemini-North/`Alopeke ({\it left}) and Keck/NIRC2 ({\it
    right}) shows an $\approx$M2V companion at $\rho \approx
    0\farcs16$, which corresponds to a projected separation of
    $53\pm4$\,au.  {\it Bottom:} Gaia EDR3 renormalized unit weight
    error (RUWE) point estimates for Kepler\,1627A and other members
    of the $\delta$\,Lyr cluster reported by \citet{KounkelCovey2019}.
    Since other members of the cluster with similar colors have
    comparable degrees of photometric variability, the high RUWE
    suggests that Kepler\,1627 is an astrometric binary. 
    \label{fig:kep1627binary}
	}
\end{figure*}

We first noted the presence of a stellar neighbor in archival
Keck/NIRC2 Kp-band adaptive optics imaging (2.12\,$\mu $m), from the
Spring semesters of both 2015 and 2019.  We acquired additional
Gemini-North/`Alopeke speckle imaging on 24 June 2021, which showed
the same companion in the 0.83\,$\mu$m notch filter, but not the
$0.56\,\mu$m filter.  Figure~\ref{fig:kep1627binary} summarizes the
results of the high-resolution imaging.  Although the companion is
unresolved in the Gaia source catalog, its existence was also
suggested by the primary star's large RUWE, relative to other members
of the \cn.  The images yield a projected separation $\rho \approx
0\farcs16$, with $\Delta m_{832} \approx 3.1$ and $\Delta m_{\rm Kp} =
2.5$.  Using the measured Gaia EDR3 parallax for the system, this
implies a projected separation of $53 \pm 4$\,au.  Given the large
observed RUWE of the primary, and the low geometric probability that a
companion imaged within $\rho \approx 0\farcs16$ is a chance
line-of-sight companion, we proceed under the assumption that the
companion is bound, and that Kepler\,1627 system is a binary.  Based
on the
tabulation\footnote{\url{http://www.pas.rochester.edu/~emamajek/EEM_dwarf_UBVIJHK_colors_Teff.txt},
version \texttt{2021/03/02}.} by \citet{pecaut_mamajek_2013}, the
measured magnitude differences for a G8V primary correspond to a
spectral type for the companion of $\approx$M2V ($M_\star \approx
0.44\,M_\odot$).  However, the companion should have a longer
pre-main-sequence contraction phase than the primary, which would
imply that this mass is overestimated by $\sim10$ to $20\%$.
